a and generators

### 2022-03-31 documentos/kraus.tex
quito comments ya hablados con Carlos

Lindblad processes arise naturally in many theoretical~\cite{lindblad,kossa,kossa2,Gorini1976,cirac,davalosdivisibility} and
experimental~\cite{PhysRevA.67.042322} \ddnote{aqui hace falta buscar mas citas, estoy buscando algo relacionado con la optical master equation, el pedo es que creo que esas ondas son time-dependent} settings and are archetypical in decoherence dynamics. \ddnote{añado esto a ver si gusta, motiva el hecho de que los PCEs sean puntos limite y no "puntos intermedios"} {\blue Moreover, these processes lead to a monotonically lose of information~\cite{breuerreview} and describe non invertible channels in the asymptotic limit $t\to \infty$ (this can be seen from the monotonically decreasing of the determinant, see Ref.~\cite{cirac}).}
It is known that not every quantum channel can be seen as a snapshot of a
process
arising from a traditional Lindblad equation or even a time-dependent Lindblad
equation~\cite{cirac,davalosdivisibility}. 
Therefore, an interesting question is whether \pce{} channels can be seen as limit points of
some Markovian processes. In this section we prove what in fact they are, and
give two examples of Markovian implementations.
%
The first
one consist in identifying each \pce{} channel as a fixed point of some pure
dissipative process. The second, in identifying each \pce{} channel as fixed
points of some memory-less collision model.

>>>>

Lindblad processes arise naturally in many theoretical~\cite{lindblad,kossa,kossa2,Gorini1976,cirac,davalosdivisibility} and
experimental~\cite{PhysRevA.67.042322} settings and are archetypical in decoherence dynamics. Moreover, these processes lead to a monotonically lose of information~\cite{breuerreview} and describe non invertible channels in the asymptotic limit $t\to \infty$ (this can be seen from the monotonically decreasing of the determinant, see Ref.~\cite{cirac}).
It is known that not every quantum channel can be seen as a snapshot of a
process
arising from a traditional Lindblad equation or even a time-dependent Lindblad
equation~\cite{cirac,davalosdivisibility}. 
Therefore, an interesting question is whether \pce{} channels can be seen as limit points of
some Markovian processes. In this section we prove what in fact they are, and
give two examples of Markovian implementations.
%
The first
one consist in identifying each \pce{} channel as a fixed point of some pure
dissipative process. The second, in identifying each \pce{} channel as fixed
points of some memory-less collision model.
